\documentclass{article}
\usepackage[hmargin=1.0cm, vmargin=1.5cm]{geometry}
\thispagestyle{empty}
\pagestyle{empty}
\begin{document}
\begin{minipage}[t]{3.8in} 
\vspace{-30pt}
\section *{\Huge Sheetal Umesh Kumar} 
\vspace{28pt}
 \section*{Work Experience}
     {\bf Spotify, New York City, NY} \\
      {\bf Software Engineer,  Feb 2013 - Apr 2015} 
      \begin{itemize}
      \item
     Built a suite of internal tools for content ingestion, man-
agement and QE validation using AngularJS and Java.
       \item
     Implemented the user profile page for iOS using
HTML/CSS/JS and wrote map reduce jobs to study user
engagement with the user profile page.
      \end{itemize}
      {\bf Ideeli Inc, New York City, NY} \\
      {\bf Software Engineer, Jul 2011 - Nov 2012}
      \begin{itemize}
      \item
      Raised new visitor conversions five-fold by streamlining the customer registration process.      
      \item
      Fixed a broken credit card authorisation system, retaining customers who otherwise would be unable to make purchases.
      \item 
      Replaced a legacy returns/refunds system with a more robust implementation.
      \item
      Implemented many other features, including a favourites section, an address book, product recommendations and tools for internal users.
      \item
      Implemented performance metrics measurement for the digital asset management system. Improved site-wide performance by serving assets from the CDN and spritifying images to reduce HTTP requests, etc. 
      \item
       Improved front-end testing by introducing Jasmine and integrating it into Ideeli's test suite. 
       \end{itemize}
      {\bf Enter: New media, New York City, NY} \\
      {\bf Software Engineer,  Dec 2010 - Apr 2011} 
      \begin{itemize}
      \item
      Worked on a reporting and analytics system using Lift+Scala+MongoDB, to provide reporting features for clients and partner companies.
      \end{itemize}
      {\bf Children's Progress, New York City, NY} \\
      {\bf Software Engineer, Jan 2009 - Dec 2010} 
      \begin{itemize}
      \item
      Developed majority of the user interface code for a web 2.0 admissions assessment application. 
      \item
      Lead developer for an award winning customer support application used to manage 200,000 users. Designed the interface with input from the customer support team and implemented the views and controllers(of MVC).  
      \item
      Created features for an interactive reporting application used by teachers and administrators.
            \item
      Ported a desktop assessment application to run on the web using XULRunner.
      \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{3.4in}  
 \begin{tabular}{rrr}
   \vspace{0pt}
   \emph {17 Lasher Ln, Edgewater NJ 07093} \\
   \emph {972-809-3704} \\
   \emph {sheetaluk@gmail.com } \\
   \emph {github.com/sheetaluk } \\
 \end{tabular}
  \vspace{-5pt}
  \section*{Skills}
    \begin{itemize}
      \item {\bf Languages/DBs:} Ruby, Php, Python, Java, C,
Javascript, Cassandra, MySQL, Postgres, Riak,
HTML, CSS
      \item {\bf Frameworks/Libraries:} AngularJS, Flask,
Rails, CakePHP, JQuery, Jasmine, QUnit, Back-
bone, LessCSS
      \item {\bf Tools/Misc:} Emacs, Bash, Grunt, Git, Mercurial,
SVN, SBT, Maven, Jenkins, \LaTeX
      \item {\bf OS:} Linux, Mac
    \end{itemize}
     
  \section*{Education}
   {\bf Master of Science, Computer Science} \\
    {\bf Dec 2008} \\ 
    University of Texas at Dallas \\
    Dallas, TX \\
    
    {\bf University of Texas at Dallas, Dallas, TX }\\
      {\bf Research Assistant, Sep 2006 - Jul 2007}
      \begin{itemize}
    \item
      Developed a web crawler in Java to  \\ search science journals for manuscripts/abstracts containing search terms using. 
      \item 
      Conducted research on various topics in \\ Bioinformatics including text mining to study protein-protein interaction by sequence pattern.
    \end{itemize}
    {\bf Academic projects}
      \begin{itemize}
        \item A web server with the PIC 16F84 chip
        \item A floppy sized distribution of Linux
        \item Various database management systems
        \item OS mutual exclusions and recovery protocols\\
      \end{itemize}
          
    {\bf Bachelor of Engineering, Computer Science} \\
    {\bf Aug 2005} \\
    Vishweshwariah Technological university \\
    Mysore, India
    
\end{minipage}
\end{document}